6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-22 paper.tex
Fixed up some evaluation stuff

The streaming event service is designed to collect metrics from a large number of monitored hosts and report any significant changes back to the management API\@. A language with strong support for concurrency and high throughput networking would be ideal for this problem. Ruby has relatively poor support for the above features, as it generally lacks support for non-blocking operations, and has a number of flaws with multi-threading, such as the `Global Interpreter Lock" problem~\cite{RubyGIL}. In contrast, languages such Java and Clojure\footnote{See http://clojure.org for a full description of Clojure} have far better support for this type of application.

@@

Standard measures of system reliability are calculated at the service level, for example `Mean Time Between Failure" (MTBF) and `Mean Time To Recovery" (MTTR), these measures give a good indication of how often and how serious any issues are. These measures can be supplemented at the UI level with other measures from Graphite, such as service uptime/availability.

@@

Ansible is one of the simplest configuration management tools around. Its competitors, Chef and Puppet, provide significantly more functionality that is not required for this project. Many of the features of Chef and Puppet allow them to efficiently orchestrate changes on large numbers of hosts, and offer more features for platform agnosticism, this carries some extra complexity. Ansible is a simpler variant more suitable for a small number of nodes, and its simplicity makes writing `playbooks" quick and painless.

Ansible `playbooks" are declared in YAML format. Ansible contains specific modules for most types of configuration task, usually implemented as thin wrappers around UNIX commands. It builds in checks to ensure that commands are idempotent. This allows the user to repeatedly use a playbook with no negative effects on the host. The playbooks look similar to the following:

@@

    Thirdly, the tool is not yet available as a `Software as a Service' offering, but if this is pursued at a later date, each instance of the tool must be isolated from the other, so as to avoid any leaking of data between users. Generally, it may be safer to run many instances of the application using virtualization, so as to be sufficiently isolated from other users.

@@

\begin{itemize}
  \item A large number of events accumulated within the system, causing a significant delay when loading the Web UI. Some problematic checks were fixed, and the amount of data returned from the API significantly reduced, fixing the problem completely.
  \item Connectivity issues between the host and the management API are quite common, often only lasting for a few seconds. The main solution to this was to increase the time window before a previous event had been declared `expired". Setting the event validity period to approximately 3 times the check interval allows for up to three consecutive lost packets, more indicative of a real problem.
  \item The number of alerts produced is inversely proportional to their value. If alerts are triggered with zero tolerance for failures, the system administrator is unreasonably burdened with issues which will resolve themselves in a few minutes. This results in failures being ignored, or the disabling of checks completely. Incidents now trigger after a short delay, increasing the confidence in a real problem and collecting extra information before alerting the system administrator.
\end{itemize}

@@

    Justification.

>>>>

The streaming event service is designed to collect metrics from a large number of monitored hosts and report any significant changes back to the management API\@. A language with strong support for concurrency and high throughput networking would be ideal for this problem. Ruby has relatively poor support for the above features, as it generally lacks support for non-blocking operations, and has a number of flaws with multi-threading, such as the ``Global Interpreter Lock" problem~\cite{RubyGIL}. In contrast, languages such Java and Clojure\footnote{See http://clojure.org for a full description of Clojure} have far better support for this type of application.

@@

Standard measures of system reliability are calculated at the service level, for example ``Mean Time Between Failure" (MTBF) and ``Mean Time To Recovery" (MTTR), these measures give a good indication of how often and how serious any issues are. These measures can be supplemented at the UI level with other measures from Graphite, such as service uptime/availability.

@@

Ansible is one of the simplest configuration management tools around. Its competitors, Chef and Puppet, provide significantly more functionality that is not required for this project. Many of the features of Chef and Puppet allow them to efficiently orchestrate changes on large numbers of hosts, and offer more features for platform agnosticism, this carries some extra complexity. Ansible is a simpler variant more suitable for a small number of nodes, and its simplicity makes writing ``playbooks" quick and painless.

Ansible ``playbooks" are declared in YAML format. Ansible contains specific modules for most types of configuration task, usually implemented as thin wrappers around UNIX commands. It builds in checks to ensure that commands are idempotent. This allows the user to repeatedly use a playbook with no negative effects on the host. The playbooks look similar to the following:

@@

    Thirdly, the tool is not yet available as a ``Software as a Service' offering, but if this is pursued at a later date, each instance of the tool must be isolated from the other, so as to avoid any leaking of data between users. Generally, it may be safer to run many instances of the application using virtualization, so as to be sufficiently isolated from other users.

@@

\begin{itemize}
  \item A large number of events accumulated within the system, causing a significant delay when loading the Web UI. Some problematic checks were fixed, and the amount of data returned from the API significantly reduced, fixing the problem completely.
  \item Connectivity issues between the host and the management API are quite common, often only lasting for a few seconds. The main solution to this was to increase the time window before a previous event had been declared ``expired". Setting the event validity period to approximately 3 times the check interval allows for up to three consecutive lost packets, more indicative of a real problem.
  \item The number of alerts produced is inversely proportional to their value. If alerts are triggered with zero tolerance for failures, the system administrator is unreasonably burdened with issues which will resolve themselves in a few minutes. This results in failures being ignored, or the disabling of checks completely. Incidents now trigger after a short delay, increasing the confidence in a real problem and collecting extra information before alerting the system administrator.
\end{itemize}

@@

    The interface is clear and simple. Where it has been demonstrated, users gave overwhelmingly positive feedback on usability and understanding, especially in comparison to existing monitoring tools such as Nagios.
